Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations

### 2024-06-30 main.tex
numerous updates

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{email2@example.com}} \and
    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
}

@@

Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
We review some of the main outcomes. 
% TODO: wait for answer to email 
Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}. Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates. 
% 
The literature knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that can circumvent the effect of low boundary regularity~\cite{vohralik2005discrete,ern2021finite}. 
These potentials share being constructed step-by-step: 
starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is complete. That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest. 
The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
along the interfacing intersection, the two potentials will only differ by a constant, 
and that difference can easily be removed to ensure continuity across that interface. 
% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.

@@

% Exterior calculus 
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus. Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights structures common to the gradient, curl, and divergence operators. It also enables us to leverage on the rich literature of Sobolev spaces of differential forms. For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
\\

@@

In the Hilbert space case, $p=2$, the work of Guerini and Savo shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary. These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains. % TODO: double check

@@

% % TODO:V&V seems to be the only reference for stars .... General results of this type for a class containing the finite element stars are not known to us. In particular and as will be illustrated in a moment, Poincar\'e constants of stars and thus of star-shaped domains may be arbitrarily large. Consequently, corresponding bounds have to incorporate some quantity that perceives the possible lack of convexity. % TODO: \cite{vohralik2005discrete}

% Estimates for Poincare constants 
% \cite{bebendorf2003note}
% \cite{vohralik2005discrete}
% Verfurth, Veeser & Verfurth 
% ...

@@

Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
In practice, we not always distinguish between points and singleton simplices. % TODO: see whether being formally correct is possible 
Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.

@@

We know optimal Poincar\'e--Friedrichs constants over convex domains~\cite{ferone2012remark,esposito2013poincare}: 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
% TODO: double check what is known in the literature 
Note that the last inequalities imply, again when $1 \leq p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
Finally, since convex domains are Lipschitz domains: 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains,
While the underlying idea remains the same, the construction of the potential is slightly different. 
As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
when homogeneous boundary conditions are imposed on a single face of the boundary. 
% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,p}
        \leq 
        \left( C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p} \right),  
        \quad 
        C_{{\rm PF},T,F,p}
        \leq 
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
        %\diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

    The second inequality follows from Rademachers theorem when $p = \infty$.
    Let assume that $1 \leq p < \infty$. 
    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
    Without loss of generality, $F$ lies in the span of the first $n-1$ coordinates and the $n$-th coordinate is non-negative over $T$. 
    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $u$ outside of $T$.
    With the fundamental theorem of calculus and H\"olders inequality: 
    \begin{align*}
        &
        \int_{\Omega} |u(x_{1},\dots,x_{n-1},x_{n})|^{p} dx_1 \dots dx_{n-1} dx_{n}
        \\&
        \leq
        \int_{\Omega} \left| \int_{0}^{x_n} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{n}
        \\&
        \leq
        \int_{\Omega} \int_{0}^{x_n} x_{n}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
        \\&
        \leq
        \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
        \leq 
        D^{p} 
        \int_{\Omega} |\nabla u|^{p} dx
        .
    \end{align*}
    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.

@@

% TODO: https://arxiv.org/html/1607.08163v3
% https://mathoverflow.net/questions/403415/properties-a-triangulation-must-have-in-order-to-describe-a-manifold

@@

% TODO: we only need some basic properties, namely that the construction maintains manifolds with boundary.
% TODO: copy and adapt the content of Ziegler and Kozlov as necessary
% The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}

@@

% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars

@@

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
They are defined by 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \det(\Jacobian\phi) \Jacobian\phi^{-1} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{align}
\end{subequations}
where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
These mappings are invertible. 
%
% TODO: bounds
%
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{align}
\end{subequations}
for $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
    \end{CD}
\end{align*}

@@

    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr

@@

    \vol_{n-1}(S_1) \int_0^D r^{k} dr

@@

%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr

@@

%     \vol_{n-1}(S_1) \int_0^D r^{k} dr

@@

% TODO: Density of C infty mit oder ohne c. 
% TODO: Density im kernel 
% TODO: lrcorner

@@

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

\title{Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{email2@example.com}} \and
    Martin Vohral\'ik\thanks{Affiliation of the Third Author, \texttt{email3@example.com}}
}

@@

Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
We review some of the main outcomes. 
Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}. Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates. 
% 
The literature knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that can circumvent the effect of low boundary regularity~\cite{vohralik2005discrete,ern2021finite}. 
These potentials share being constructed step-by-step: 
starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is complete. That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest. 
The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
along the interfacing intersection, the two potentials will only differ by a constant, 
and that difference can easily be removed to ensure continuity across that interface. 
% Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.

@@

% Exterior calculus 
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}. Exterior calculus is used ubiquitously in physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights structures common to the gradient, curl, and divergence operators. It also enables us to leverage on the rich literature of Sobolev spaces of differential forms. For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
\\ % hu2019structure

@@

In the Hilbert space case, $p=2$, the work of Guerini and Savo shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary. These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex Lipschitz domains.

@@

@@

Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. 
In practice, we not always distinguish between points and singleton simplices. 
Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (codimension $1$ members) of this triangulation.

@@

We know optimal Poincar\'e--Friedrichs constants over convex domains~\cite{ferone2012remark,esposito2013poincare}: 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
Note that the last inequalities imply, again when $1 \leq p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
Finally, since convex domains are Lipschitz domains: 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

We also want to assess an alternative route towards Poincar\'e--Friedrichs inequalities over triangulated domains,
While the underlying idea remains the same, the construction of the potential is slightly different. 
As an auxiliary result with independent relevance, we compute an upper bound for the Poincar\'e--Friedrichs inequality 
when homogeneous boundary conditions are imposed on a single face of the boundary. 
We present this result with two different techniques. 
While it may not be obvious, the second estimate is tighter than the first estimate when using the optimal Poincar\'e--Friedrichs constants for convex domains. 
% Upper bounds for the classical Poincar\'e inequality over a simplex is widely known.

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,p}
        \leq 
        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
        \quad 
        C_{{\rm PF},T,F,p}
        \leq
        \frac{1}{\sqrt[p]{p}}
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
        %\diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

    The second inequality follows from Rademacher's theorem when $p = \infty$.
    Let assume that $1 \leq p < \infty$. 
    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
    Without loss of generality, 
    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
    and the minimal first coordinate among all the points of $F$ equals $0$. 
    We write $\bfg \in \bfL^{\infty}(T)$ be the trivial extension of $\nabla u$ outside of $T$.
    %With the fundamental theorem of calculus and H\"olders inequality: 
    \begin{align*}
        \int_{\Omega} |u(x)|^{p} dx
        &\leq
        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} dx_{1} d\overline{x}
        \\&
        \leq
        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| dy \right|^{p} dx_{1} d\overline{x}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} dx_{1}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} dx_1 \cdot \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} dy d\overline{x} 
        \leq
        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} dx
        %
%         \leq
%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} dx_1 \dots dx_{n-1} dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) dy \right|^{p} dx_1 \dots dx_{n-1} dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} dy dx_1 \dots dx_{n-1} dx_{n}
%         \leq 
%         D^{p} 
%         \int_{\Omega} |\nabla u|^{p} dx
%         .
    \end{align*}
    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.

@@

@@

@@

@@

We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
They are defined by 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \det(\Jacobian\phi) \Jacobian\phi^{-1} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{align}
\end{subequations}
where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
These mappings are invertible. 
%
% TODO: bounds on the Jacobian transform 
%
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{align}
\end{subequations}
for $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
    \end{CD}
\end{align*}

@@

    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr

@@

    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr

@@

%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr

@@

%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr

@@

% DONE: Density of C infty mit oder ohne c.

@@

\begin{proposition}\label{proposition:guerinisavo}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded domain. Then 
    Moreover, 
    \begin{align*}
        C_{\rm{PF},\Omega,0,2} \geq C_{\rm{PF},\Omega,1,2} \geq \dots \geq C_{\rm{PF},\Omega,n-1,2}
    \end{align*}
\end{proposition}
\begin{proof}
    The result is true if $\Omega$ has a smooth boundary. 
    Now suppose that $\Omega$ is a Lipschitz domain. 
\end{proof}
